Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-09 VegOzone.tex
Move model describtion and gap-filling to appendix

\section{DO3SE modeling}
\label{sec:do3se}
To investigate which of the environmental factors might be most influential in determining \chem{O_3} damage; such as that observed on clover and tobaccos in 2018, we model ozone uptake of different natural and semi-natural vegetation using the $\mathrm{DO_3SE}$ model and develop bespoke subarctic parameterizations for common plant species. We first give an account of the $\mathrm{DO_3SE}$ model, input data, and the used methodology for deriving the bespoke parameters. Then we will present and discuss the modeling results.

@@

\section{DO3SE parameterization}

\begin{figure*}[t]
  \includegraphics[width=12cm]{figB1}
  \caption{Estimated begin (BGS) and end (EGS) of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (\unit{doy}) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure*}

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_evergreen}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_evergreen}
  \includegraphics[width=12cm]{figB2}
\caption{Construction of bespoke response functions for Norway spruce. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_spruce}
\end{figure}

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_birch}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_birch}
  \includegraphics[width=12cm]{figB3}
\caption{Construction of bespoke response functions for downy birch. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_birch}
\end{figure}

>>>>

\section{DO3SE modeling}
\label{sec:do3se}
To investigate the difference between 2018 and 2019 concerning stomatal ozone uptake and to assess which of the environmental factors might be most influential in determining \chem{O_3} damage risk, we model ozone uptake of different natural and semi-natural vegetation using the $\mathrm{DO_3SE}$ model and develop bespoke subarctic parameterizations for common plant species. We the $\mathrm{DO_3SE}$ model and gapp-filling methods are described in Appendix~\ref{sec}. First, we give an account of the methodology for deriving bespoke parameters. Then, we will present and discuss the modeling results.

@@

\section{DO3SE model}
\label{appendix:do3se_model}

\subsection{Bespoke parameterizations}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{figB1}
  \caption{Estimated begin (BGS) and end (EGS) of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (\unit{doy}) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure}

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_evergreen}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_evergreen}
  \includegraphics[width=8.3cm]{figB2}
\caption{Construction of bespoke response functions for Norway spruce. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_spruce}
\end{figure}

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_birch}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_birch}
  \includegraphics[width=8.3cm]{figB3}
\caption{Construction of bespoke response functions for downy birch. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_birch}
\end{figure}
